Sakura Blossom Prediction Model for Japan

### 2024-12-03 paper/paper.qmd
Done!

The main outcome variables in this study are the "flowering day" and "full bloom day," which represent the specific dates (converted into numeric form) when sakura enters the flowering and full bloom stages, respectively. A statistical summary of these variables is presented in @tbl-flower-sta, while @fig-flower depicts their overall distribution. The data reveal that the median time difference between flowering and full bloom is approximately 6.22 days. Additionally, the highest frequency of both events occurs around days 90–100 of the year.

@@

## Survey design and sampling techniques
The survey design of this study integrates historical and modern sakura blossom datasets, providing a powerful framework for analyzing long-term trends and regional differences. And analyzed a survey from Statista on the purpose of visiting Japan, with over 32,364 participants, of which 13% of tourists came specifically for sakura blossoms [@arba2024travel]. The historical data, spanning 812 CE to 2015, focuses on Kyoto, where flowering dates have been reconstructed using historical documents, such as diaries and records of hanami events. These reconstructions were validated against observed data starting in 1881, ensuring reliability.

>>>>

The main outcome variables in this study are the "flowering day" and "full bloom day", which represent the specific dates (converted into numeric form) when sakura enters the flowering and full bloom stages, respectively. A statistical summary of these variables is presented in @tbl-flower-sta, while @fig-flower depicts their overall distribution. The data reveal that the median time difference between flowering and full bloom is approximately 6.22 days. Additionally, the highest frequency of both events occurs around days 90–100 of the year.

@@

## Sampling, Data Observational and Potential Bias
The survey design of this study integrates historical and modern sakura blossom datasets, providing a powerful framework for analyzing long-term trends and regional differences. And analyzed a survey from Statista on the purpose of visiting Japan, with over 32,364 participants, of which 13% of tourists came specifically for sakura blossoms [@arba2024travel]. The historical data, spanning 812 CE to 2015, focuses on Kyoto, where flowering dates have been reconstructed using historical documents, such as diaries and records of hanami events. These reconstructions were validated against observed data starting in 1881, ensuring reliability.
